\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Additional custom settings here...

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Allen Li} \\ \vspace{1pt}
    \small 778-896-8628 $|$ \href{mailto:allenli9417@gmail.com}{\underline{allenli9417@gmail.com}} $|$ 
    \href{https://linkedin.com/in/allen-li-5667b8248}{\underline{linkedin.com/in/allen-li-5667b8248}} $|$
    \href{https://github.com/Allenli33}{\underline{github.com/Allenli33}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {British Columbia Institute of Technology}{Vancouver, BC}
      {Computer Information Technology Diploma (CIT) GPA: 86/100}{Jan 2022 -- Dec 2023}
    \resumeSubheading
      {Kwantlen Polytechnic University}{Vancouver, BC}
      {General Studies}{Sep. 2017 -- Sep 2019}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Impact North Shore}{North Vancouver, BC}
      {IT Support Specialist}{Jan 2025 – Present}
      \resumeItemListStart
      \resumeItem{Provide frontline IT support, troubleshooting hardware, software, and network issues to enhance service accessibility.}
      \resumeItem{Install, configure, and maintain IT infrastructure, including MS Windows, MS 365, and cloud-based tools.}
      \resumeItem{Train staff on IT security best practices, software usage, and digital literacy to improve technology adoption.}
      \resumeItem{Manage IT asset inventory, including hardware, software, and licenses, ensuring accurate tracking and compliance.}
      \resumeItem{Monitor and resolve IT support tickets, analyzing trends to improve system reliability and user experience.}
    \resumeItemListEnd
      

  \resumeSubHeadingListEnd    % Add more projects here...

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: \textbf{Python}, \textbf{JavaScript}, HTML/CSS, SQL, Bash, R} \\
     \vspace{2mm}  % Adjust the space as needed

     \textbf{Frameworks/Libraries}{: Flask, React, NextJS, Node.js, pandas, NumPy} \\
     \vspace{2mm}  % Adjust the space as needed

     \textbf{Tools \& Platforms}{: Docker, Kubernetes, Git, Postman, Apache-jmeter, Terraform, Ansible, Cloud Computing (AWS, Azure, Google Cloud), sonarqube Kafka, MongoDB, MySQL, Nginx, Linux} \\
     \vspace{2mm}  % Adjust the space as needed

     \textbf{DevOps \& CI/CD}{: Jenkins, GitLab-CI, emphasizing CI/CD practices for streamlined deployment processes} \\
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

  \resumeProjectHeading
  {\textbf{Personal Web Portfolio} $|$ \emph{React, Next.js, Tailwind CSS}}{Recent Project}
  \resumeItemListStart
    \resumeItem{Developed a comprehensive portfolio website, showcasing projects, skills, and educational background.}
    \resumeItem{Utilized React and Next.js for efficient client-side rendering and seamless page transitions.}
    \resumeItem{Integrated Tailwind CSS for responsive and aesthetically pleasing design.}
    \resumeItem{Implemented dynamic content rendering using React hooks to manage state transitions and UI updates.}
    \resumeItem{Featured sections include detailed project descriptions, a downloadable resume, and contact information, accessible at \href{https://www.allenli-portfolio.com}{allenli-portfolio.com}.}
  \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{Library Microservices} $|$ \emph{Python, Flask, Kafka, Docker, MySQL, Nginx}}{Sep 2023 -- Dec 2023}
      \resumeItemListStart
        \resumeItem{Architected a distributed library management system, optimizing for scalability and resilience.}
        \resumeItem{Facilitated inter-service communication via Kafka, ensuring robust data exchange and system integrity.}
        \resumeItem{Leveraged Docker for containerization, achieving consistent deployments and isolated environments.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Network Provisioning with Terraform and Ansible} $|$ \emph{Terraform, Ansible, AWS}}{Sep 2023 -- Dec 2023}
      \resumeItemListStart
        \resumeItem{Orchestrated a cloud-based infrastructure on AWS, utilizing Terraform for infrastructure as code practices.}
        \resumeItem{Automated configuration and deployment of EC2 instances and network resources with Ansible, enhancing operational efficiency.}
      \resumeItemListEnd

  

    \resumeProjectHeading
      {\textbf{Flappy Patrick} $|$ \emph{Python, Pygame, Flask}}{Sep 2022 -- Dec 2022}
      \resumeItemListStart
        \resumeItem{Engineered a Flappy Bird clone, enhancing gameplay with real-time scoring and dynamic obstacles.}
        \resumeItem{Devised APIs for game state management and score tracking, employing Flask for server-side logic.}
        \resumeItem{Implemented JSON for efficient data serialization and storage, optimizing game performance.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd






\end{document}
