%-------------------------
% Resume in Latex
% Author : Hao Li
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Additional custom settings here...

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Allen Li} \\ \vspace{1pt}
    8800 Hazelbridge Way, Richmond, BC, V6X0S3 \\
    \small 778-896-8628 $|$ \href{mailto:allenli9417@gmail.com}{\underline{allenli9417@gmail.com}} $|$ 
    \href{https://linkedin.com/in/allen-li-5667b8248}{\underline{linkedin.com/in/allen-li-5667b8248}} $|$
    \href{https://github.com/Allenli33}{\underline{github.com/Allenli33}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {British Columbia Institute of Technology}{Vancouver, BC}
      {Computer Information Technology Diploma (CIT) GPA:86/100}{Jan 2022 -- Dec 2023}
      \resumeSubheading
      {Kwantlen Polytechnic University}{Vancouver, BC}
      {General Studies}{Sep. 2017 -- Sep 2019}
  \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Flappy Patrick} $|$ \emph{Python, Pygame, Flask, HTML, JSON}}{Sep 2022 -- Dec 2022}
      \resumeItemListStart
        \resumeItem{Developed a Flappy Bird clone with Python and Pygame, featuring real-time scoring and gameplay mechanics.}
        \resumeItem{Implemented a Flask server for score management and a web interface using HTML for score display.}
        \resumeItem{Integrated JSON for data handling and storage, and managed HTTP requests for score updates.}
        \resumeItem{Used object-oriented programming for effective game state and interaction management.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{GPA Calculator (Group Project)} $|$ \emph{Python, Flask, MongoDB, PyMongo, HTML, CSS, JavaScript}}{May 2022}
      \resumeItemListStart
        \resumeItem{Contributed to a collaborative GPA calculator, managing user data with Flask and MongoDB.}
        \resumeItem{Focused on frontend development using HTML/CSS for a responsive user interface.}
        \resumeItem{Implemented bcrypt for secure authentication and user registration features.}
        \resumeItem{Scrum-based Agile methodologies for iterative development and team collaboration.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Library Microservices} $|$ \emph{Python, Flask, Kafka, Docker, MySQL, Nginx, Connexion, YAML  }}{Sep 2023 -- Dec 2023}
      \resumeItemListStart
        \resumeItem{Designed a library management system using a microservices architecture for various operational functions.}
        \resumeItem{Used Kafka for inter-service communication and MySQL for data storage and retrieval.}
        \resumeItem{Containerized services using Docker, ensuring consistent deployment across environments.}
        \resumeItem{Configured Nginx for request routing and load balancing across microservices.}
      \resumeItemListEnd

      \resumeProjectHeading
      {\textbf{Network Provisioning with Terraform and Ansible} $|$ \emph{Terraform, Ansible, AWS }}{Sep 2023 -- Dec 2023}
      \resumeItemListStart
        \resumeItem{Designed and provisioned an AWS-based infrastructure using Terraform for services including EC2, RDS, S3, and VPC.}
        \resumeItem{Configured EC2 instances for web and backend services using Ansible, ensuring efficient and secure operations.}
        \resumeItem{Automated setup of security groups, routing tables, and subnets to streamline network architecture.}
        \resumeItem{Managed dynamic inventory and role-based configurations in Ansible for scalable deployment of services.}
        \resumeItem{Developed Ansible playbooks for consistent and automated configuration of Nginx and MySQL services.}
      \resumeItemListEnd


  \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {YVR World Dufry Duty-Free}{Vancouver, BC}
      {Retail Sales}{August 2019 – April 2020}
      \resumeItemListStart
        \resumeItem{Demonstrated excellent service to customers with clothing, shoes and accessories.}
        \resumeItem{Improved customer satisfaction and boosted sales record.}
        \resumeItem{Built strong communication, teamwork skills and the ability to learn fast.}
        \resumeItem{Managed cash and credit payments and adhered to cash handling policies and regulations.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd    % Add more projects here...


%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, HTML, CSS, SQL, Bash} \\
     \textbf{Frameworks/Libraries}{: Flask, React, Node.js, pandas, NumPy, Matplotlib} \\
     \textbf{Tools \& Platforms}{: Docker, Kubernetes, Git, GitHub, GitLab, Terraform, Ansible, Azure Cloud, AWS (EC2, RDS, S3, VPC), Kafka, Pygame, MongoDB, PyMongo, MySQL, Nginx, Linux, Windows OS, VS Code, PyCharm, Virtual Machines, Google Cloud Platform} \\
     \textbf{DevOps \& CI/CD}{: Jenkins, Gitlab-CI, Continuous Integration, Continuous Deployment} \\
     \textbf{Methodologies}{: Agile, Scrum, Object-Oriented Programming (OOP), Microservices Architecture} \\
     \textbf{Soft Skills}{: Strong communication, Team collaboration, Problem-solving, Fast learning, Adaptability, Fluent in English and Mandarin}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
